Generalization Errors of Hard Parameter Sharing: High-dimensional Asymptotics and Implications

### 2020-10-04 arxiv/proof_examples.tex
revise

&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}}  +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\

@@

 Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
 \begin{align*}
 & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
 &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,
 \end{align*}
 where
 \begin{align*}
&h_1(A):=  (\beta_1-A\beta_2)^\top (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)  ,\\
& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon_1}  ,\\
& h_3(A):=  A^2 { (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
& h_4(A):=  (\epsilon^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1), \\
&h_5(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1),\\
&h_6(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
\end{align*}
Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.

For $h_1(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability:
\begin{align*}
&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right| \\
&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \\
&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \\
&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2),
\end{align*}
for any small constant $\e_1>0$. Here in the last step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
\begin{align*}
&\left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \\
&\le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \Sigma(A)^{-1} \right\|^2 \lesssim \frac{p}{(A^2+1)^2}.
\end{align*}

@@

\paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
\begin{align*}
L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \\
&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,
\end{align*}
where we denoted
$$\hat \Sigma:= \hat A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
To illustrate the idea of bias-variance decomposition, we assume that $\hat A$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now. Then we can calculate the partial expectation of $L(\hat{\beta}_2^{\MTL})$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
 \begin{align}
	&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2,\beta_1,\beta_2} \nonumber \\
&	=  \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 \nonumber\\ %\label{eq_bias_2task} 
			& + \sigma^2\cdot \bigtr{ X^{(2)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(2)})^\top}+ \sigma^2\cdot \hat A^2 \bigtr{ X^{(1)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(1)})^\top}\nonumber\\
			%+\sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } \nonumber\\ 
			&= \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).\nonumber
			%\label{eq_var_2task}
\end{align}
This gives a bias-variance decomposition of the MTL prediction loss: the first term on the right-hand side is the bias term, while the second term is the variance term. For the random-effects model, we further take the partial expectation over $\beta_1$ and $\beta_2$: 
 \begin{align}
	\exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}&	=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} }\nonumber \\
	&+\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
			\label{eq_var_2task}
\end{align}
One can compare the above expression with the predication loss for STL, that is,
\begin{align}
	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
\end{align}
we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over the second term on the right-hand side of equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!

@@

%control the difference between $g(A)$ and its partial expectation. 
 \begin{claim}\label{claim_largedev2}
 In the setting of Proposition \ref{cor_MTL_loss}, if $\hat A=\OO(1)$, then we have that with high probability,
$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat A)\right| \le p^{-1/2+e}\cdot p\left(\sigma^2 +\kappa^2 +d^2 \right),$$
for any small constant $e>0$. Here we introduced the function
\begin{align*}
	\cal L(\hat A)	:=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} } +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
\end{align*}
 \end{claim}
 \begin{proof}
 \todo{add proof}
 \end{proof}

>>>>

&+  A^2 \exarg{ \epsilon^{(2)}}{ (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} \\
& +A^2 \exarg{ \epsilon^{(1)}} { (\epsilon^{(1)})^\top X^{(1)} \Sigma(A)^{-1}  (X^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top \epsilon^{(1)}  }\\

@@

 Now we expand the first term on the right-hand side of \eqref{eq_mtl_A12}: 
 \begin{align*}
 & \left\| X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1)+ \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)} + A X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)} \right\|^2 \nonumber\\
 &=h_1(A) + h_2(A) +h_3(A) + 2h_4(A) + 2h_5(A) + 2h_6(A) ,
 \end{align*}
 where
 \begin{align*}
&h_1(A):=  (\beta_1-A\beta_2)^\top (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (\beta_1-A\beta_2)  ,\\
& h_2(A) := {(\epsilon^{(1)})^\top \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)^2\epsilon^{(1)}}  ,\\
& h_3(A):=  A^2 { (\epsilon^{(2)} )^\top X^{(2)} \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)}\Sigma(A)^{-1} (X^{(2)})^\top \epsilon^{(2)}} , \\
& h_4(A):=  (\epsilon^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1), \\
&h_5(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} (A\beta_2-\beta_1),\\
&h_6(A):=A (\epsilon^{(2)})^\top X^{(2)}\Sigma(A)^{-1} (X^{(1)})^\top\left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right)\epsilon^{(1)}.
\end{align*}
Next we estimate each term using Lemma \ref{largedeviation} in Appendix \ref{app_tool}.

For $h_1(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool} and the fact that the entries of $\beta_1-A\beta_2\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variance $p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]$, we obtain the following estimate with high probability for any small constant $\e_1>0$:
\begin{align}
&\left|h_1(A) - \exarg{\beta_1,\beta_2}{h_1(A) \mid X_1, X_2}\right|\nonumber \\
&\le p^{\e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F \nonumber\\
&\le p^{e_1}\cdot p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]\cdot p^{1/2} \left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \nonumber \\
&\lesssim p^{1/2+e_1}\cdot \frac{(A-1)^2\kappa^2 + (A^2+1)d^2/2}{(A^2+1)^2}\lesssim p^{1/2+e_1}(\kappa^2 + d^2).\label{eq_hA1}
\end{align}
 Here in the third step we used \eqref{op_X12} and \eqref{op_Sig1} to bound the operator norm:
\begin{align*}
&\left\| (X^{(2)})^\top X^{(2)}  \Sigma(A)^{-1}  (X^{(1)})^\top X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\| \\
&\le \left\| (X^{(2)})^\top X^{(2)}\right\|^2 \cdot \left\| (X^{(1)})^\top X^{(1)}\right\|\cdot \left\| \Sigma(A)^{-1} \right\|^2 \lesssim \frac{p}{(A^2+1)^2}.
\end{align*}  
Similarly, using Lemma \ref{largedeviation}, the fact that the entries of $\epsilon^{(1)},\epsilon^{(2)}\in \R^p$ are i.i.d. Gaussian random variables with mean zero and variances $\sigma^2$, and bounds \eqref{op_X12}-\eqref{op_Sig1}, we can obtain that with high probability,
\be\label{eq_hA23}\left|h_2(A) - \exarg{\epsilon^{(1)}}{h_2(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2, \quad \left|h_3(A) - \exarg{\epsilon^{(2)}}{h_3(A) \mid X_1, X_2}\right| \lesssim p^{1/2+\e_1}\sigma^2.\ee
For $h_4(A)$, using Lemma \ref{largedeviation} in Appendix \ref{app_tool}, we obtain the following estimate with high probability for any small constant $\e_1>0$:
\begin{align}
\left|h_4(A)\right| &\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]}\cdot \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|_F\nonumber \\
&\le p^{e_1}\cdot \sigma \sqrt{p^{-1}[(A-1)^2\kappa^2 + (A^2+1)d^2/2]} \cdot p^{1/2} \left\| \left(A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top-\id_{n_1}\right) X^{(1)} \Sigma(A)^{-1} (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{e_1}\cdot \sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2} \cdot \left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\cdot  \left\|X^{(1)}\right\| \left\|\Sigma(A)^{-1}\right\|\left\| (X^{(2)})^\top X^{(2)} \right\|  \nonumber\\
&\lesssim p^{1/2+e_1}\frac{\sigma \sqrt{ (A-1)^2\kappa^2 + (A^2+1)d^2/2}}{A^2+1} \lesssim p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2),\label{eq_hA4}
\end{align}
where in the fourth step we used $\left\|  \id_{n_1}-A^2 X^{(1)}\Sigma(A)^{-1} (X^{(1)})^\top\right\|\le 1$ and \eqref{op_X12}-\eqref{op_Sig1}, and in the last step we used AM-GM inequality. With same argument, we can show that 
\be\label{eq_hA56} \left|h_5(A)\right| \le p^{1/2+e_1}(\sigma^2 + \kappa^2 + d^2), \quad \left|h_6(A)\right| \le p^{1/2+e_1}\sigma^2,\ee
with high probability for any small constant $e_1>0$. %Combining \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, we conclude that

Finally, we can obtain similar estimates for the second term on the right-hand side of \eqref{eq_mtl_A12} as in  \eqref{eq_hA1}, \eqref{eq_hA23}, \eqref{eq_hA4} and \eqref{eq_hA56}, which conclude the proof of Claim \ref{claim_largedev1}.
 \end{proof}

@@

\paragraph{Calculating the prediction loss.} Now we calculate the predication loss using the optimal $\hat B$ in equation \eqref{eq_Bhat_2task} and optimal $\hat A=\hat A_1/\hat A_2$:
\begin{align}
L(\hat{\beta}_2^{\MTL}) &=\left|\Sigma_2^{1/2} \left( \hat B \hat A_2 - \beta_2\right)\right| \nonumber\\
&=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,\label{Lbeta_HPS}
\end{align}
where we denoted
$$\hat \Sigma:= \hat A^2 (X^{(1)})^\top X^{(1)}  + (X^{(2)})^\top X^{(2)} .$$
To illustrate the idea of bias-variance decomposition, we assume that $\hat A$ is independent of $\epsilon^{(1)}$, $\epsilon^{(2)}$, $\beta_1$ and $\beta_2$ for now. Then we can calculate the partial expectation of $L(\hat{\beta}_2^{\MTL})$ over the randomness in $\epsilon_1$ and $\epsilon_2$:
 \begin{align}
	&\exarg{\epsilon^{(1)}, \epsilon^{(2)}}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2,\beta_1,\beta_2} \nonumber \\
&	=  \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 \nonumber\\ %\label{eq_bias_2task} 
			& + \sigma^2\cdot \bigtr{ X^{(2)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(2)})^\top}+ \sigma^2\cdot \hat A^2 \bigtr{ X^{(1)} \hat\Sigma^{-1}\Sigma^{(2)}\hat\Sigma^{-1} (X^{(1)})^\top}\nonumber\\
			%+\sigma^2\cdot \bigtr{\Sigma_2(\frac{W_1^2}{W_2^2} X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} } \nonumber\\ 
			&= \bignorm{(\Sigma^{(2)})^{1/2}\hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} (\hat A \beta_1 - \hat A^2\beta_2)}^2 +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).\nonumber
			%\label{eq_var_2task}
\end{align}
This gives a bias-variance decomposition of the MTL prediction loss: the first term on the right-hand side is the bias term, while the second term is the variance term. For the random-effects model, we further take the partial expectation over $\beta_1$ and $\beta_2$: 
 \begin{align}
	\exarg{\epsilon^{(1)}, \epsilon^{(2)},\beta_1,\beta_2}{L(\hat{\beta}_2^{\MTL}) \mid X_1, X_2}&	=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} }\nonumber \\
	&+\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
			\label{eq_var_2task}
\end{align}
One can compare the above expression with the predication loss for STL, that is,
\begin{align}
	\exarg{\epsilon_2}{L(\hat{\beta}_2^{\STL}) \mid X_2} = \sigma^2 \cdot \bigtr{\Sigma_2 (X_2^{\top} X_2)^{-1}}, \label{eq_var_stl}
\end{align}
we observe that while the bias of $\hat{\beta}_2^{\MTL}$ is always larger than that of $\hat{\beta}_2^{\STL}$, which is zero, the variance of $\hat{\beta}_2^{\MTL}$ is always lower than that of $\hat{\beta}_2^{\STL}$.\footnote{To see why this is true, we apply the Woodbury matrix identity over the second term on the right-hand side of equation \eqref{eq_var_2task} and use the fact that for the product of two PSD matrices, its trace is always nonnegative.}
In other words, training both tasks together helps predict the target task by reducing variance while incurring a bias.
Therefore, whether multi-task learning outperforms single-task learning is determined by the bias-variance decomposition!

@@

%control the difference between $g(A)$ and its partial expectation. 
 \begin{claim}\label{claim_largedev2}
 In the setting of Proposition \ref{cor_MTL_loss}, if $\hat A=\OO(1)$, then we have that with high probability,
$$\left| L(\hat{\beta}_2^{\MTL})- \cal L(\hat A)\right| \le p^{-1/2+e}\cdot p\left(\sigma^2 +\kappa^2 +d^2 \right),$$
for any small constant $e>0$. Here we introduced the function
\begin{align*}
	\cal L(\hat A)	:=  \left[(\hat A-1)^2 \kappa^2 + (\hat A^2+1)\frac{d^2}2\right] \cdot p^{-1}\bigtr{ (X^{(1)})^{\top}X^{(1)} \hat\Sigma^{-1} \Sigma^{(2)} \hat\Sigma^{-1} (X^{(1)})^{\top}X^{(1)} } +\sigma^2\cdot \tr\left(\Sigma^{(2)}\hat \Sigma^{-1}\right).
\end{align*}
 \end{claim}
 \begin{proof}
 The proof of this claim is the same as the one for Claim \ref{claim_largedev1}, so we only give an outlier of proof without writing down all the details. We expand $L(\hat{\beta}_2^{\MTL}) $ in \eqref{Lbeta_HPS} as:
 \begin{align*}
\cor L(\hat{\beta}_2^{\MTL}) &=  \left\| (\Sigma^{(2)})^{1/2}\hat \Sigma^{-1} \left[(X^{(1)})^\top X^{(1)} (\hat A\beta_1-\hat A^2\beta_2)+ (X^{(2)})^\top \epsilon^{(2)} + \hat A   (X^{(1)})^\top \epsilon^{(1)} \right]\right\|^2,
\end{align*}
 \end{proof}
